Synthesizing by means of mice

### 2020-07-27 mice_synthesizing/Mice_Synthesizing.Rmd

```{r, fig.fullwidth = TRUE, dpi = 500}
mice_df <- data.frame(term = cart_fit$var, df = cart_fit$df)
syn_df <- data.frame(term = pooled$term, df = pooled$df)

@@

@@

```{r, echo = F}
true_results
synthetic_results
```

>>>>

```{r, fig.fullwidth = TRUE, dpi = 1000}
mice_df <- data.frame(term = cart_fit$var, df = cart_fit$df)
syn_df <- data.frame(term = pooled$term, df = pooled$df)

@@

norm_results <- boot_cart %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %>%
  mutate(df = NA,
         lower = est - qnorm(.975) * sqrt(var),
         upper = est + qnorm(.975) * sqrt(var)) %>%
  ci_cov(truemodel) %>%
  kable(digits = 3, caption = "Normal CI approximation") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

@@

```{r, echo = F}
true_results
synthetic_results
norm_results
